---
title: "How to Upload a File via FTP in R"
author: "D"
date: "08 settembre 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())

```

Ever wondered how to upload a file to an FTP server in R?

## Here's how!
Let's suppose you have an acount named __*user_name*__, with password: __*user_password*__ by the ftp server with address: __*ftp.server.com*__.

To upload the local file named: __*origin_filename.ext*__ to the ftp server, in the folder: __*dest_folder*__, having name: __*destination_filename.ext*__, you simply hit:

```{r include = TRUE, eval = FALSE}
library(RCurl)

ftpUpload("origin_filename.ext", "ftp://user_name:password@ftp.server.com/dest_folder/destination_filename.ext")

```

## This even works with DataCamp's R console!

Unfortunately, sometimes DataCamp's R console does not allow to run the command:
```{r}
library(RCurl)
```

In this case you can use this function:
```{r}
upload_ftp <- function(file, url, verbose = FALSE){

  con <- file(file, open = "rb")
  on.exit(close(con))
  h <- curl::new_handle(upload = TRUE, filetime = FALSE)
  curl::handle_setopt(h, readfunction = function(n){
    readBin(con, raw(), n = n)
  }, verbose = verbose)
  curl::curl_fetch_memory(url, handle = h)
}

```

providing the to be uploaded filename as the file parameter, and the classical string:
"ftp://user_name:password@ftp.server.com/dest_folder/destination_filename.ext"

for the url parameter

Credits: This solution is based on Jim Hester's devtools implementation (https://github.com/jimhester)
