---
title: "Untitled"
author: "D"
date: "09 settembre 2016"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
rm(list = ls())
setwd("C:\\Nuova cartella\\Data Camp - Text Mining in R")

```

```{r}
tweets <- read.csv("coffee.csv", stringsAsFactors = FALSE, header = TRUE)

```

Our corpus of data is composed of: `r dim(tweets)[1]` tweets records each composed of `r dim(tweets)[2]` observations:
```{r}
names(tweets)

```

(btw: here we used the fact that function *dim* returns a vector. You can say that by: "Our corpus of data is composed of: `r nrow(tweets)` tweets records each composed of `r ncol(tweets)` observations" as well, using the *ncol* and *nrow* functions.)

More information si produced by the  *str* function:
```{r}
str(tweets)

```

Ok. Get the text from the data:
```{r}
coffee_tweets <- tweets$text
str(coffee_tweets)
class(coffee_tweets)
coffee_tweets[2]

```
*coffee_tweets* is a vector, each element of which is a text (tweet). Each tweets' text can then be accessed by usual *[ ]* operator: *coffee_tweets[2]*, and so on,

Now we want to convert it into a *corpus*, a data structure useful to mine its contents. A corpus is a collection of documents.
```{r}
library(tm)
coffee_source <- VectorSource(coffee_tweets)
str(coffee_source)

```

Since *coffee_tweets* is a vector, we use the *VectorSource* function that converts from a vector to a *Source* object. From this objects we get the corpus using the *Vcorpus* function.

This intermediate step is useul since we can convert the Source object into two types of corpuses: *VCorpus* and/or *PCorpus*. Specifically, VCorpus is a *volatile* corpus, that is a corpus that is stored in memory (ram): this is called *VCorpus*. As opposed to *PCorpus*, i.e.: permanent corpus, that is stored onto permanent sorage (disk). Other *Source* functions are provided to convert into corpus object a wide range of origin data structures.

Now let's get the corpus:
```{r}
coffee_corpus <- VCorpus(coffee_source)
print(coffee_corpus)

class(coffee_corpus)
str(coffee_corpus[[1]])
coffee_corpus[[2]]
coffee_corpus[[1]][1]$Author
```

*coffee_corpus* is a *nested list*, i.e. a list R type each element of which is a list R object by itself. The latter list elements contains 

You can get a corpus from a data frame as well. Let's get the *example_text* data frame:
```{r}
load("example_text.rda")
str(example_text)
print(example_text)

```

*DataframeSource* builds a *Source* object from a data frame. Only cols #2 and #3 of the dataframe are text, so we get source only from these cols:
```{r}
df_source <- DataframeSource(example_text[,2:3])

```
and then we get the corpus:
```{r}
df_corpus <- VCorpus(df_source)
str(df_corpus)
print(df_corpus)

```

We can consider only a single col:
```{r}
df_vector <- example_text[, 2]
vec_source <- VectorSource(df_vector)
vec_corpus <- VCorpus(vec_source)
str(vec_corpus)
print(vec_corpus)

```

# Text cleaning
```{r}
# Create the object: text
text <- "<b>She</b> woke up at       6 A.M. It\'s so early!  She was only 10% awake and began drinking coffee in front of her computer."

# All lowercase
print(tolower(text))

# Remove punctuation
print(removePunctuation(text))

# Remove numbers
print(removeNumbers(text))

# Remove whitespace
print(stripWhitespace(text))
```

```{r}
library(qdap)

```

```{r}

```

